Article Title

### 2022-04-26 paper/main/03_results.tex
docs(discussion-and-results): implications, limiations, and directions

% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
Overall features of the three dimensions in different periods are shown in Ternary, where each regime shift associates to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
% 第一阶段到第二阶段
Throughout P1, the IWGI shifts paralleled with the left axis because the Purpose indicator was barely changed and others two changed in similar trends.
Analogously, as the stress indicator unchanged during the P3, the IWGI shifts paralleled with the right axis while others two changed in opposite trends.
% 第三阶段集中
The regime then experienced a long distance shift during the P2, as three indicators changed their ratios of contribution drastically to IWGI, simultaneously.
% 总结来说，三个稳态
The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).

>>>>

% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
Overall features of the three dimensions in different periods are shown in Ternary, where each regime shift associates to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
% 第一阶段到第二阶段
Throughout P1, the IWGI shifts paralleled with the left axis because the Purpose indicator was barely changed and others two changed in similar trends.
Analogously, as the stress indicator unchanged during the P3, the IWGI shifts paralleled with the right axis while others two changed in opposite trends.
% 第三阶段集中
The regime then experienced a long distance shift during the P2, as three indicators simultaneously changed their ratios of contribution to IWGI.
% 总结来说，三个稳态
The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).

### 2022-04-26 paper/main/04_discussion.tex
docs(discussion-and-results): implications, limiations, and directions

\subsection{Water governance challenges along with transition regimes}

@@

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013). Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers.
The process echoes previous studies on how social systems can change water governance regimes by enhancing their adaptive capacity. However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition process of water governance in detail for the first time.
It is important to note that each indicator or cause changed gradually, but emergence of regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary}).

% 第一种时期(1965-1978年)，流域经济以农业为主，自然水资源相对丰富，用水治理倾向于为农业提供更多的资源。
During the massive supply regime (1965-1978), the basin economy was mainly dependent on the agriculture and natural water resources were relatively abundant (\textit{SI Appendix} Figure S5); water governance thus tended to supply more resources for agriculture (e.g. by construction of reservoirs and channels).
% 因为此时社会经济对自然水循环的影响尚且有限，几乎没有保护政策的治理体系鼓励在需供水的地区进行无节制的取水和蓄水，而很少考虑流域的社会公平。
Due to the limited effects of socio-economic feedbacks on this regime, water governance had few protective policies, assumed an unlimited water supply, and took little consideration of the impacts of water use on social equity and the environment
\cite{zhouDecelerationChinahuman2020}.
% 近80%的地表水用于供应，黄河在稳态的后半段干涸了.
Since nearly 80\% of surface water was used (mainly for provisioning purposes), the Yellow River dried up during the second half of the regime (\textit{SI Appendix} Figure S7).
% 随着干旱化的日益严重，造成了湿地萎缩、生物多样性下降等生态问题，呈现出巨大的环境危机。
Ecological issues, such as wetlands shrinkage and declines in biodiversity, emerged as the drying up became more and more serious, leading a huge social-ecological crisis and a significant challenge to existing modes of water governance rigorously
\cite{wohlfartRiverBasinCourse2016}.

% “目的转轨”的开始恰逢中国的“改革开放”，巨大的社会转型使得新兴工业和服务业打破了农业的主导地位，开始争夺水资源。
The start of the purpose-focused regime (1978) coincided with Chinese ``reform and opening-up''.
This huge social transformation led to the emergence of industry and services, broke the dominance of agriculture, and resulted in higher competition for water use (Figure~\ref{fig:Causes} and \textit{SI Appendix} Fig. S8).
% 面对遗留的环境问题和全新的经济挑战，黄河水利委员会进行了改组，接到水利部(原水电部)的指示，恢复和加强黄河水利委员会的水文、流域管理工作。
In the face of ongoing environmental challenges and new economic challenges, the Yellow River Conservancy Commission (\textit{SI Appendix} Methods S1) underwent a reorganization and received instructions from the Ministry of Water Resources (then called the Ministry of Water Resources and Electric Power) to resume and strengthen work on hydrology and basin management in the YRB
\cite{yellowriverarchivesOrganizationalHistoryYellow2004}.
% 在全国率先出台了新的政策法规(如“87调水方案”)进行调水，成功阻止了灌溉用水量的扩大。
As a result, new policies and regulations (e.g., ``the 87 Water Allocation Scheme'') were introduced in the YRB ahead of the rest of the country to allocate water for stopping the expansion of water consumption
\cite{wangThirtyYearsYellow2018}.

% 直到大约1993年以来，由于社会经济发展后先进技术的广泛应用，水资源利用效率有了显著提高，才出现了下一个政权向全面治理的转变。
The next shift, to the many-sided governance regime, did not occur until a significant increase in water use efficiency in about 1993, overcame some resource limits
\cite{liuWaterconservancyprojects2013}.
% 区域和部门之间在水需求方面的社会经济权衡在这一制度中发挥关键作用，因此水治理需要满足更全面、更有效率的水分配
Since socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalinBalancingwaterresource2015}.
% 因此，这一时期开始推广的水权转换项目，可以为其他地区的工业发展节约区域农业用水。
For example, the water rights conversion project that has been popularized during this regime may even save regional agricultural water for industrial developments in other regions, and water transfer has been another huge project to meet water demands within the YRB
\cite{barnettSustainabilityTransferproject2015,yunpengWaterRightTransfer2010}.
% 但是曾帮助流域摆脱环境危机的分水政策却在此时期成为了流域协调和社会公平的桎梏。
On the other hand, the old water policy (e.g., ``the 87 Water Allocation Scheme''), which once helped the YRB resolve its environmental crisis, limited social equity and coordinated allocation under the new regime because of path dependence
\cite{wangThirtyYearsYellow2018}.
% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
Many national-level water policies were proposed or adjusted under this regime, as the absence of such policies and social injustice in water use became new structural challenges for governance
\cite{konarExpandingScopeFoundation2019}.
%! Discussion in water transfer.

%! Discussion in which contries this method can be applied
% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
In general, shifts between the three governance regimes occurred sequentially during a transformation towards the hydrosocial cycle.
% 随着越来越多的人为影响逐渐改变世界，对生态系统动力学从生物物理控制向社会和政治控制的转变可能在社会-生态系统中变得越来越普遍
Transition from biophysical control to social and political control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
Some implications of this kind of change, when accompanied by engineering solutions, have been explored in the Millennium Assessment’s `Technogarden' scenario %! informal citation
\cite{millenniumecosystemassessmentEcosystemshumanwellbeing2005}.
% 流域转向社会-水循环的过程就是典型的社会-生态系统过渡过程，而我们发现在这一过程中水治理的稳态转换呼应了全球水治理面临的两大主要挑战。
The transition regimes identified here echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig. S9)
\cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
% 以水资源短缺和供水困难为代表的资源挑战，主要是未开发和正在开发的流域所面临的，与经济和环境变化密切相关。
Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
% 另一方面，高度控制和发达的流域主要面临结构性挑战，迫切需要在社会政策方面进行协调与合作(如水资源纠纷和缺乏合作治理，特别是跨界河流)。
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %! Kitroeff citation wrong
\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
% 非常具有代表性的是，这两类主要挑战在黄河流域快速变迁的过程中先后发生了，伴随着整合了四个维度的（经济、环境、社会、政策）治理稳态的转换。
It is typical that resource challenges and structural challenges have occurred sequentially during the transition of water governance within the YRB.
% 我们的分析表明，过渡的前期常常带来环境和经济层面的治理挑战，而在过渡的后期则主要是社会和政策层面的挑战。
Our analysis thus suggests that the initial phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
% 再一次，我们总结的框架呼应了联合国发展属为水治理提出的四个维度和两大主要问题。
From the perspective of the core dimensions emphasized by the UNDP for water governance, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.

% 随着河流流域在不同制度之间的过渡而发生的升级过程也带来了额外的挑战。在经济力量的影响下，水资源利用逐渐从一个地方性的问题转变为国家或国际的问题，大型河流流域成为生态系统服务、经济发展和人类福祉的重要来源。
Additional challenges are raised by the process of upscaling that occurs as river basins transition between regimes. Under the influence of economic forces, water use gradually changes from being a primarily local concern to becoming a national or international concern, with large river basins being critical sources of ecosystem services, economic development, and human wellbeing.
% 例如黄河小浪底调水调沙的生态系统治理需要造成下游河道迅速下切，使农民长期无法从河道中取到灌溉水资源。
For example, the requirement in the ecological system management of water and sediment diversion in the Xiaolangdi Dam of the Yellow River leads to rapid cutting of the downstream river, which makes it impossible for farmers to get irrigation water resources for a long time
\cite{kongEnvironmentalimpactassessments2017}.
% 通过升级过程成功地引导水况过渡，需要在治理机制中进行相应的升级，并创建能够调节和管理跨规模效应的更高级别机构。
Successful navigation of water regime transitions through an upscaling process requires a corresponding upscaling in the governance regime and the creation of higher-level institutions that can regulate and manage cross-scale effects
\cite{cummingScalemismatchessocialecological2006}.

\subsection{Implications and future directions} %! limitations
\label{Outlook}

%! How data obtained, how assumptions are made.
% IWGI指数以一种相对简单但全面的方式概括了水管理的过渡制度。
The IWGI index captures the transitional regimes of water governance in a relatively simple but comprehensive way.
% 对科学家和决策者来说，认识到不断变化的治理挑战是重要的，因为发展并不是解决所有与可持续性有关的流域问题的万能药
It is important for scientists and decision makers to recognize the changing governance challenges, because development is not a panacea for all basin issues regarding sustainability. %! 完全是陈词滥调
%! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
% 在一种制度下开发的模型和方法在另一种制度下不一定有用。
Models and approaches developed under one regime are not necessarily useful under a different regime.
% 就当今世界而言，与水有关的挑战仍是我们在实现可持续性方面取得进展的主要差距之一，而发展优先战略在许多地方仍是主导方针，可能不利于改善治理
For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
\cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}.
% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
% 总的来说，这种明显的治理失败可能有两个主要原因。
Overall, there are probably two main reasons for this apparent failure of governance.
% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
\cite{graftonparadoxirrigationefficiency2018}.
% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
Second, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
\cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
From these perspectives, we need better and more comprehensive strategies to address governance challenges because the core problems are complex and difficult to manage
\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.

>>>>

\subsection{Challenges along with transition of water governance regimes}

@@

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013). 
Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, then decide who gets water, when and how.
The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
However, the IWGI quantitatively identifies and reveals that conceptual pattern, thus characterizing the transition of water governance in detail for the first time.
It is important to note that each indicator or cause changed gradually, but emerging regime shifts moves water governance along with the hydrosocial water cycle at a basin scale.
As a result, the challenges were primarily economic and environmental at the beginning of the YRB's water governance trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).

% 在水资源压力较低的大规模供应制度(长江流域1965-1978年)期间，水治理实践倾向于通过建设水库和渠道来增加服务用水(当时主要是供应目的——牲畜和农作物)。
During the massive supply regime with lower water stress (1965-1978 in the YRB), water governance thus practices tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by construction of reservoirs and channels.
% 然而，正如“人类将征服自然”的流行口号所暗示的那样，水供应的增加很少考虑到人水关系不可逆转的变化，从而也急剧增加了水的需求，很少考虑到流域的保护。
As the the popular slogan ``man will conquer nature'' suggested, however, the enhancement of water supply aligned with little consideration of the irreversible changes of human-water relationship, thus also drastically increased water demand with few consideration in basinal conservation. 
\cite{zhouDecelerationChinahuman2020}.
% 在那十年里，灌溉农田和引水设施的迅速扩张，使负担过重的长江水利枢纽接近临界点，在这个临界点上，持续增加供应来满足无限的需求是不现实的
The rapid expansion of irrigated farmland and water diversion facilities in that decade brought the overburdened YRB close to the critical point, where keeping increasing supply to meet the unlimits of demand is unpractical
% 结果，自1972年以来，超过80%的地表水使用量导致了河流的频繁枯竭，随之而来的是生态问题，如湿地的萎缩和生物多样性的下降。
As a result, the over 80\% surface water use then led to depletions of the river frequently since 1972, with ecological issues, such as wetlands shrinkage and declines in biodiversity. 
% 此外，由于处于上升阶段的工业经济也受到水资源压力的限制，现有的水治理模式严重导致了巨大的社会-生态危机和对可持续性的重大挑战
In addition, as the industrial economy in the ascendant was also limited by the water stress, the existing modes of water governance led a huge social-ecological crisis and a significant challenge to sustainability rigorously
\cite{wohlfartRiverBasinCourse2016}.

The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``openning and reform''.
% 正如理论预测的那样
The results in the YRB keep in line with the suggestions from theorical analysis: continuous increases in water demand when the basinal total supply is stable can be accompanied by large changes in governance regime and the rapidly enhancement in overall social adaptive capacity.
% 作为制度转变的先行者
Being a pioneer in shifting governing institution, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfering plan and so on
\cite{wangThirtyYearsYellow2018}.
% 因此，1999年黄河的最后一次枯竭
As a consequence, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnotes to the climax of this transformation in water governance.

Finally, it came into an adaptation-oriented regime (P3: 2002-2013), when drastically shifting in societies occurred with a stable water stress.
Socio-economic trade-offs between water-dependent regions and sectors played a more important role at this regime, so water governance had to achieve efficient water allocation while balancing different purposes in the face of limited water supply
\cite{dalinBalancingwaterresource2015}.
Reconstruction of resources widespread in different industries and regions was calling for adaptation in water governance, where the widespread requirements of adjusting in the rigid quota shares from the previous regime can be an example.
% 类似的，此稳态下国家层面的水治理政策都在进行补充或调整，因为这种制度的缺失和社会的不公平正成为流域新的治理挑战。
Like this, much national-level water governing practices were proposed under the regime, because the absence of such policies with social dilemma of high quality development became new structural challenges for water governance
\cite{konarExpandingScopeFoundation2019}.

% 一般来说，在向水社会循环的转变过程中，三种治理制度之间的转变是依次发生的。
In general, shift between the governance regimes advances in parallel with the trajectory of hydrosocial cycle (Figure~\ref{fig:summary}A, B and C).
Transition from biophysical control to social and institutional control of ecosystem dynamics may become increasingly widespread in social-ecological systems as increasing anthropogenic impacts gradually change the world
\cite{bestPaceHumanInducedChange2020,cummingLinkingeconomicgrowth2018,cummingImplicationsagriculturaltransitions2014}.
With intensive anthropogenic intervention, the YRB may be the most prominent example in this general transition of water governance -``improving supply, transforming governance, and enhancing adaptation'' %! citation.
The transition regimes identified here also echo the two kinds of major water governance challenges globally (resource challenges and structural challenges, Figure~\ref{fig:summary} and \textit{SI Appendix} Fig. S9)
\cite{singhWaterGovernanceChallenges2019,porcherFacingChallengesWater2019}.
Our analysis suggests that the early phase of transition often leads to resource-focused challenges that result from economic, demographic and environmental change; while later phases are dominated by structural challenges relating to social and political aspects of governance.
Resource challenges, represented as water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins and are highly related to economic and environmental changes
\cite{allanNavigatingcomplexitiescoordinated2019,florkeWatercompetitioncities2018,liuWaterSustainabilityChina2012}.
Alternatively, highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures %! Kitroeff citation wrong
\cite{kitroeffThisWarCrossBorder2020,kitroeffThisWarCrossBorder2020,roobavannanRoleSectoralTransformation2017,unep-dhiTransboundaryRiverBasins2016}.
It is typical that resource challenges and structural challenges occurred sequentially during the transition of water governance within the YRB.
From the perspective of the core dimensions emphasized by the UNDP for water governance, therefore, our proposed schema connects governance challenges and the transformation of large river basins towards a hydrosocial water cycle.

\subsection{Implications, limitations, and future directions}
\label{Outlook}

% Implications
Water governance gradually changes from being a primarily local concern to becoming a national or international concern, because large river basins being critical sources of ecosystem services, economic development, and human wellbeing. 
As the ubiquitous tele-coupling are rising additional challenges of water governance in the tighter connected world, where transition between regimes aligns with different human-water relationships. 
Within the growing hydro-social cycle, the IWGI index captures the increasment of the adaptive capacity and sketches the transitional regimes of water governance, in a relatively straightforward but comprehensive way.
It is important for scientists and decision makers to recognize the changing governance challenges, because models, institutions, engineerings, and approaches developed under one regime are not necessarily useful under a different regime
%! \cite{cummingLinkingEconomicGrowth2018, reyersSocialEcologicalSystemsInsights2018}.
In the case of the YRB, an important institutions of water quota in the governance tranforming regime became rigid during the enhanced adaptation phase.
On contrary, additional water from the ambitious cross-basins water diversion project, which originated in the phase of massive supply can play an even more crucial role in today's enhancing adaptation phase.
Overall, applications of IWGI can induce a straightforward understanding of the water governance in transition of hydrosocial cycle, as descriptions from some previous conceptual frameworks suggested for all large-scale basins worldwide.

%! limitations
One of the main limitations of applying IWGI in abundant data availability for a long-term period of time. 
For an example, we used the stress-flexibility-variability (SFV index) here, one of the most comprehensive index to our knowledge, as an indicator of the water stress dimension. 
With other indicators, therefore, we obtained various datasets in the YRB: water use in different regions and sectors, streamflows in different reaches, reservoir capacity and completion time, with further more information in social, economic, and institutional for interpretation.
It means still a gap between the comprehensively identifying and widespread application of IWGI.
However, we assumed that all solutions of water governance are relative to the question of ``who gets water, when and how'', so water stress, purposes of water services, and patterns of water allocation are matters.
We suggest that choices of the indicators for the dimensions can be adapted according to available datasets as the intertwines between the underlying components are much more crucial in understanding the transition of governance regimes.

% direction
For today's world, water-related challenges remains one of the major gaps in our progress towards sustainability, while development-first strategies are still a dominant guideline in many places and may be in opposition to improving governance
\cite{xuAssessingprogresssustainable2020,liuAerosolweakenedsummermonsoons2017,greveGlobalassessmentwater2018}.
% 虽然大多数大型河流流域随着发展而在水管理技术和水利用效率方面有所改善，但淡水利用仍被认为正在接近人类-水系统可能崩溃的行星边界
Although most large river basins have shown improvements in water management technologies and water use efficiency along with development, freshwater use is still considered to be approaching planetary boundaries where human-water systems may collapse
\cite{anExploringeffectsGrain2017,degraafEnvironmentalflowlimits2019,hugginssocialecologicaldimensionschanging2020}.
% 我们的分析展示了这种路径的前方很可能是严峻的水治理挑战。
% 总的来说，这种明显的治理失败可能有两个主要原因。
% Overall, there are probably two main reasons for this apparent failure of governance.
% 首先，农业灌溉效率的显著提高通常伴随着灌溉面积的重新扩大，导致水资源压力的趋势不减(效率悖论)
% First, significant improvement in agricultural irrigation efficiency is usually accompanied by a re-expansion of irrigated area, resulting in an unabated trend of water resources stress (the paradox of efficiency)
\cite{graftonparadoxirrigationefficiency2018}.
% 其次，如果没有成功的治理，以水循环为主导的复杂治理结构可能会导致流域尺度上水资源使用的灵活性降低，破坏社会-生态系统的恢复力
In the future, without successful governance, complicated governance structures dominated by hydrosocial water cycles may result in less flexible water use and undermine the resilience of social-ecological systems at a basin scale
\cite{qinFlexibilityintensityglobal2019,leviaHomogenizationterrestrialwater2020,grillMappingworldfreeflowing2019}.
% 从这些角度来看，我们需要更好、更全面的策略来应对治理挑战，因为核心问题是复杂而难以管理的
From these perspectives, we need more flexible and comprehensive strategies to address governance challenges because the core problems are dynamic and complex
\cite{steffenemergenceevolutionEarth2020,muneepeerakulemergenceresilienceselforganized2020,bodinCollaborativeenvironmentalgovernance2017,biermannNavigatingAnthropoceneImproving2012}.
% 更深入地了解包含非线性变化、制度和过渡思想的治理，应该有助于将治理的重点转移到维持流域社会-生态系统的恢复力和提高其可持续性。
A deeper understanding of governance that incorporates ideas of non-liner change, regimes, and transitions should help to shift the focus of governance towards maintaining the resilience of the basin’s social-ecological system and improving its sustainability.
